Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-03-10 01-intro.Rmd
largely completed chapters 1 and chapters 2

In many statistical applications, estimating the covariance matrix, $\Sigma$, for a set of random variables is a critical task. The covariance matrix is useful because it characterizes the *relationship* between variables. For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form

\begin{equation}
\Sigma_{xyz} = \begin{pmatrix}
1 & 0 & 0.5 \\ 
0 & 1 & 0 \\ 
0.5 & 0 & 1
\end{pmatrix}
(\#eq:ex)\notag
\end{equation}

We can gather valuable information from this matrix. First of all, we know that each of the variables has an equal variance of 1. Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0. This implies that any information in $X$ is useless in trying to gather information about $Y$. Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.

Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging. For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.

### references

The reference we need here is @molstad2017shrinking!

1. From @molstad2017shrinking: "To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated. For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors. Many authors have proposed methods that directly estimate this characteristic @cai2011direct; @fan2012road; @mai2012direct."

@@

3. Discuss linear regression application.... where $\beta = \Omega_{*}\Sigma_{*XY}$. Like @witten2009covariance, this approach estimates the regression coefficients "using shrinkage estimators of the marginal precision matrix for the predictors".

- Guide

- Model and notation

## Outline

- Why do we care about covariance matrices? Covariance matrices are an object that summarizes the relationship between variables.

- What is a precision matrix? Precision matrix is the inverse of a covariance matrix.

- Precision matrices are powerful, essential in representing relationships in variables

- In fact, required to be estimated to fit many statistical models.

- That is, we must provide an object that accurately summarizes the relationship and interaction between variables in our model.

- Many proposed shrinkage estimators when p is particularly large. Shrinkage.

- However, to fit these models, Molstad and Rothman focused on the fact that onnly a "characteristic" of a precision matrix is required to fit these models. "We propose a framework to shrink a user-specified characteristic of a precision matrix estimator."

- For instance, LDA, linear regression, ...

- Their approach/methodology was published in BLAH. Shrinking characteristic of precision matrix estimators.

- BREAK

- We wanted to explore the regression application that was mentioned but not pursued/investigated

- This document will outline the research and work leading up to that

- The document is outlined as follows...

- We will begin chapter 2 with a brief introduction to precision matrix estimation. This will include mentions of estimation methods/approaches and we will spend a particular amount of time elaborating on one approach which is estimation via the ADMM algorithm. This dicussion will be useful when we circle back to SCPME, the regression application, and the augmented ADMM algorithm developed in BLAH.

- Lastly, the document will end with two brief tutorials for the R packages ADMMsigma and SCPME. These packages, developed by myself, will be mentioned throughout the document and were instrumental in this pursued line of research and facilitated many simulations and research direction explored throughout. Both packages have since been published on CRAN

@@

There will be significant matrix algebra notation throughout the document. The trace operator which sums the diagonal elements of a matrix will take the form $tr\left(\cdot\right)$ and the *exponential* trace operator will be denoted similarly as $etr\left(\cdot\right)$. The determinant of a matrix $\mathbf{A}$ will be denoted as $\left|\mathbf{A}\right|$ but may also take the form as simply $det\left(\mathbf{A}\right)$. The kronecker product of two matrices $\mathbf{A}$ and $\mathbf{B}$ will be denoted as $\mathbf{A} \otimes \mathbf{B}$. Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as $\left\|\mathbf{A}\right\|_{F}$ and we will define $\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|$ where the $i$-$j$th element in matrix $\mathbf{A}$ is denoted as $\left(\mathbf{A}\right)_{ij}$ or simply $\mathbf{A}_{ij}$.

>>>>

In the simplest terms, inferential statistics boils down to two primary components: estimation and prediction. Estimation tends to refer to the process by which we infer properties and behavior about individual parameters. For instance, decision theory tell us that the method by which we estimate parameters should be one that incurs low risk or variance. Prediction, on the other hand, tends to refer to the process of determining the likelihood of an unknown or unforseeable event. Right now, prediction is king. The demand for good, predictive models has sparked huge investments in research and given rise to communities - like the machine learning community - whose primary goal is establishing good predictive models.

However, though prediction is getting a lot of attention, these two components are not entirely distinct and often go hand-in-hand. In fact, the success of many predictive models is largely contingent upon the ability to be efficient and proficient in estimation. That is, the succces and reliability of prediction is often a product of good estimation.

For instance, many statistical models require the estimation of the co-variability and interaction between variables. This statistical object often comes in the form of a precision matrix ($\Omega$) - or the inverse of the covariance matrix. For this reason, in the last decade there has been an ever-expanding community devoted to matrix precision estimation. Like the covariance matrix, the precision matrix offers a powerful way of presenting the covariance - or pairwise variability between any two random variables.

Fisher's linear discriminant analysis (LDA) is one of these statistical models. Under the assumption of normal data, the model aims to classify observations into two or more populations of data.

The central theme of this thesis is on precision matrix estimation but also expanding on a paper written by Aaron Molstad and Adam Rothman in 2017. In this paper, @molstad2017shrinking focused on the fact that only a "characteristic" of a precision matrix is required to fit these models.

- From @molstad2017shrinking: "To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated. For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors. Many authors have proposed methods that directly estimate this characteristic @cai2011direct; @fan2012road; @mai2012direct."

@@

With the goal of improving performance..

They offer a framework to do other things...

Their approach/methodoloy was published in BLAH. Shrinking Characteristic of precision matrix estimators.

The purpose of this work began with the desire to expand on the work in @molstad2017shrinking and to explore avenues that were mentioned but were not further investigated. One of these research directions was the application of their shrinking characteristics approach to regression. However, in order to get to that point and to build up the knowledge to understand and contribute new material, there were a number of concepts that needed to be understood along the way. This document will follow that journey.

We will begin chapter 2 with a brief introduction to the area of precision matrix estimation and the gaussian log-likelihood function. This section will include mentions of other estimation methods and algorithms but most discussion we will spent on the ADMM algorithm. This discussion will be useful when we begin elaborating on the shrinking characteristics approach (sometimes referred to as SCPME), the augmented ADMM algorithm, and later the application to regression. Lastly, the document will end with two brief tutorials for the R packages `ADMMsigma` and `SCPME`. These packages were developed by myself to aid in simulation experiments and make it easier to branch into related research directions. Both packages have since been published on CRAN.

@@

There will be significant matrix algebra notation throughout the document. The trace operator which sums the diagonal elements of a matrix will take the form $tr\left(\cdot\right)$ and the *exponential* trace operator will be denoted similarly as $etr\left(\cdot\right)$. The determinant of a matrix $\mathbf{A}$ will be denoted as $\left|\mathbf{A}\right|$ but may also take the form as simply $det\left(\mathbf{A}\right)$. The kronecker product of two matrices $\mathbf{A}$ and $\mathbf{B}$ will be denoted as $\mathbf{A} \otimes \mathbf{B}$ and the element-wise product will be denoted as $\mathbf{A} \circ \mathbf{B}$. Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as $\left\|\mathbf{A}\right\|_{F}$ and we will define $\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|$ where the $i$-$j$th element in matrix $\mathbf{A}$ is denoted as $\left(\mathbf{A}\right)_{ij}$ or simply $\mathbf{A}_{ij}$.

### 2019-03-10 02-PME.Rmd
largely completed chapters 1 and chapters 2

### Literature Review?

- Articles that review covariance and precision matrix estimation in high dimensional settings are @pourahmadi2013high and @fan2016overview.

- The person who initially proposed the lasso-penalized gaussian likelihood precision matrix estimation is @yuan2007model.

- Other authors who have proposed methods with non-lasso penalizations are (Frobenius norms) @witten2009covariance, @rothman2014existence, (non-convex penalties) @lam2009sparsistency, and @fan2009network.

- Standard alternating direction method of multipliers approaches are found in @boyd11distributed.

- ADMM with modification based on majorize-minimize principle is found in @lange2016mm.

- Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.

- L1-penalized gaussian likelihood precision matrix estimator (@yuan2007model; @rothman2008sparse; @friedman2008sparse).

@@

Consider the case where we observe $n$ independent, identically distributed copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Omega^{-1}$. That is, $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$.

Because we assume independence, we know that the probability of observing these specific observations $X_{1}, ..., X_{n}$ is equal to

@@

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. It follows that the log-likelihood for $\mu$ and $\Omega$ is equal to the following:

@@

If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n$ which we typically denote as $\bar{X}$. However, in addition to $\mu$, many applications require the estimation of $\Sigma$ as well. We can also find a maximum likelihood estimator:

\begin{equation}
\begin{split}
\hat{\Omega}^{mle} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ const. + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right] \right\} \\
  &= \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)' \right]^{-1}
\end{split}
(\#eq:omegamle)\notag
\end{equation}

By setting the gradient equal to zero and plugging in the MLE for $\mu$, we find that the MLE for $\Omega$ is the inverse our usual sample estimator for the covariance matrix, denoted here as $S^{-1}$. It turns out that we could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$ and taken its inverse:

\begin{equation}
\hat{\Omega}^{mle} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
(\#eq:omegamlesimple)
\end{equation}

so that $\hat{\Omega}^{MLE} = S^{-1}$. Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$^[Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood. Both procedures will result in the same estimate.].

As in regression settings, we can construct a *penalized* log-likelihood estimator by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that

@@

$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$. These penalties are the ridge and lasso, respectively.

## ADMM algorithm

Many efficient methods have been proposed to solve for $\hat{\Omega}$ when $\alpha = 1$. The most popular method is the graphical lasso algorithm (glasso) introduced by @friedman2008sparse. However, no methods (to the best of my knowledge) have estimated $\Omega$ when $\alpha \in (0, 1)$. We will use the alternating direction method of multipliers (ADMM) algorithm to do so.

As the authors state in @boyd2011distributed, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers." For our purposes, we will only focus on the ADMM algorithm but it is encouraged to read the original text from Boyd and others for a complete introduction to the other two methods.

@@

\vspace{3cm}

In the `ADMMsigma` package, we instead take

so that solving the full penalized log-likelihood for $\Omega$ results in solving

where $0 \leq \alpha \leq 1$. This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] and is identical to the penalty used in the popular penalized regression package `glmnet`. Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty. Having this flexibility and generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.

@@

>>>>

@@

The foundation of much of the precision matrix estimation literature is the gaussian negative log-likelihood. We consider the case where we observe $n$ independent, identically distributed (iid) copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Omega^{-1}$. That is, $X_{i}$ follows a $p$-dimensional normal distribution $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$. Note that this formulation implies that $\mu \in \mathbb{R}^{p}$, $\Omega^{-1} \in \mathbb{S}_{+}^{p}$, and the probability of observing a single $X_{i}$ is

\begin{equation} 
  f\left(X_{i}; \mu, \Omega^{-1}\right) = (2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] 
(\#eq:normallikone)\notag
\end{equation}

Furthermore, because we assume pairwise independence between each observation, we know that for a sample of size $n$, the probability of observing all $X_{1}, ..., X_{n}$ is equal to

@@

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. Therefore, the gaussian log-likelihood for $\mu$ and $\Omega$ can be written as

@@

It is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n \equiv \bar{X}$, so that the partially maximized gaussian log-likelihood for $\Omega$ can be written as

\begin{equation}
\begin{split}
  l(\Omega | X) &= \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)'\Omega \right] \\
  &= \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
(\#eq:partialmaxloglik)\notag
\end{split}
\end{equation}

where $S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n$ is the usual sample estimator for the covariance matrix.

In addition to $\mu$, we could also find the maximum likelihood estimator for $\Omega$ and use that as our estimator. By setting the gradient of the partially maximized log-likelihood equal to zero, we find that

\begin{equation}
\begin{split}
\hat{\Omega}^{MLE} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left(S\Omega \right) \right\} \\
  &= \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \\
  &= S^{-1}
\end{split}
(\#eq:omegamle)\notag
\end{equation}

so that the MLE for $\Omega$, when it exists, is $\hat{\Omega}^{MLE} = S^{-1} = \left[\sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n \right]$. The reality, however, is that this object does *not* always exist. In settings where the number of observations is exceeded by the number of features in a sample, the sample covariance matrix, $S$, is rank deficient and no longer invertible.

For this reason, many papers in the last decade have proposed shrinkage estimators of the precision matrix similar to the shrinkage estimators in regression settings. That is, instead of minimizing solely the negative log-likelihood function, authors have proposed minimizing the gaussian log-likelihood *plus* a penalty - often a function of the precision matrix. These methods effectively force the eigen values of the precision matrix, $\Omega$, to be strictly greater than zero.

@@

This penalty, which we will denote as $P\left(\Omega\right)$, is typically a variation of the ridge penalty $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or the lasso penalty $P\left(\Omega \right) = \lambda\left\|\Omega\right\|_{1}$. The authors, @yuan2007model, were the ones who initially proposed precision matrix estimation by the lasso-penalized gaussian likelihood which they originally defined as

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\sum_{i \neq j}\left|\Omega_{ij}\right| \right\}
(\#eq:omegapenlasso)
\end{equation}

so as not to penalize the diagonal elements of the precision matrix estimate. Other papers published on the lasso-penalized gaussian likelihood precision matrix estimator include @rothman2008sparse and @friedman2008sparse and many efficient algorithms have been proposed to solve for $\hat{\Omega}$ in this setting. However, the most popular method is still the graphical lasso algorithm (sometimes referred to as glasso) introduced by @friedman2008sparse. Their method utilizes an iterative block-wise coordinate descent algorithm that builds upon the coordinate descent algorithm use in lasso regression.

Other papers published that propose methods with non-lasso penalizations like the Frobenius norms include @rothman2014existence, @witten2009covariance, and @price2015ridge. In fact, the latter two papers show that the estimation procedure can be solved in closed-form. Non-convex penalties were considered in @lam2009sparsistency and @fan2009network.

The penalty we will explore here and in the next section is one that is a convex combination of the lasso and the ridge penalties:

where $0 \leq \alpha \leq 1$ is an additional tuning parameter (similar to $\lambda$). Clearly, when $\alpha = 0$ this penalty reduces to a ridge penalty and when $\alpha = 1$ it reduces to a lasso penalty. This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] in the context of regression and is the penalty used in the popular penalized regression package `glmnet`. However, no published work has explored the elastic-net penalty in the context of precision matrix estimation. This penalty allows for increased flexibility and we will show how to solve the following optimization problem in the next section using the ADMM algorithm.

## ADMM Algorithm

ADMM stands for the alternating direction method of multipliers and this algorithm was largely popularized by Stephen Boyd and his fellow authors in the book *Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers* [@boyd2011distributed]. As the authors state in the text, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers."

The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications.

@@

@@

@witten2009covariance; @price2015ridge

### 2019-03-10 03-SCPME.Rmd
largely completed chapters 1 and chapters 2

### literature review?

- - Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.

###  other stuff

@@

*This section requires general knowledge of the alternating direction method of multipliers (ADMM) algorithm. I would recommend reading this overview I have written [here](https://mgallow.github.io/ADMMsigma/articles/Details.html#admm-algorithm) before proceeding.*

The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications. Within the context of @molstad2017shrinking, this algorithm would consist of iterating over the following three steps:

@@

with $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$. However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function ($\tilde{L}$) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form.

@@

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)\notag
(\#eq:approx)
\end{split}
\end{equation}

@@

since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$. Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[Proof of BLAH in section BLAHHH].

@@

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{align}

>>>>

@@

Within the context of @molstad2017shrinking, this algorithm would consist of iterating over the following three steps:

@@

with $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$. However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function ($\tilde{L}$) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form. The ADMM algorithm with modification based on majorize-minimize principle is also found in @lange2016mm.

@@

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)
(\#eq:approx)
\end{split}
\end{equation}

@@

since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$. Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[Further explanation of majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
(\#eq:augADMM)\notag
\end{split}
\end{equation}
